---
title: "Desirability and price perception"
author: "Moniek"
date: "4/7/2020"
output: ingmarkdowntemplates::ing_html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# to run this script: open result (for individual level) & test combi between historie and 2020 data 
```


## Deepdive price perception vs desirability

<br><br>
The aim of this overview is to get better understanding of the relation between the perception consumers have of the prices in the market and desirability. 

* Desirability: “If fees were no object, which of the brands would you choose?”  
* Price perception: "could you rank the brands on a scale from not expensive to expensive"

Both questions as evaluated on a scale from 0-100 where people are asked to rank the brands they are familair with (max 5 brands). 

Because of the formulation of the desirability question, a direct relation between price perception and desirability is not expected. To evaluate the premium value of the brand, price is not a factor for desirability. To understand the impact of price perception on people's choice, preference is explored as well. A reasonable set of possible independent variables are taken into account. 

**First impression based on aggregated data (Jan 2020)** <br>
To get an idea of the current market situation in each country, desirability is plotted against price perception. This provides an overview of how expensive people *think* a brand is, against which brand they would choose if money was no object. Obviously, being considered as not expensive increases the chance that people actually will prefer the brand. Desirability is the brand they choose if money was no object, the higher the better. 

**Correlation analysis individial level** <br>
To explore the relationships better, an analysis on individual respondent level is performed. This is relevant to lower the error which allows stronger conclusions. The relationship between price perception and desirability is performed regardless of the brand and specifically for ING per market. 

<br><br>

### Overview per country
<br>
<div class="row">  

  <div class="col-md-4" markdown="1"> <br>
```{r AUS, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==1) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
  layout(title = 'Australia', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
  </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r AUT, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==2) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'Austria', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
  </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r BEL, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==3) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
  layout(title = 'Belgium', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
  </div>  
</div> 

  <div class="col-md-4" markdown="1"> <br>
```{r CZE, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==4) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'Czech', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
  </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r FRA, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==5) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'France', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
  </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r GER, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==6) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'Germany', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
  </div>  
</div> 

  <div class="col-md-4" markdown="1">  <br> 
```{r ITA, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==7) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'Italy', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
 </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r LUX, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==8) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'Luxembourg', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
 </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r POL, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==9) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
  layout(title = 'The Netherlands', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
   </div> <div class="row">  
</div> 

  <div class="col-md-4" markdown="1">  <br>
```{r ROM, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==10) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'Poland', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
 </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r SPA, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==11) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
  layout(title = 'Romania', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
 </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r NL, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==12) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
  layout(title = 'Spain', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
   </div> <div class="row">  
</div> 

  <div class="col-md-4" markdown="1">  <br>
```{r TPH, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==13) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'Turkey', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
 </div>
  
  <div class="col-md-4" markdown="1">
  <br>
```{r TUR, eval=T, echo=F, fig.width=4, fig.height=4, warning=FALSE}
desi_comb <- test %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==14) %>%
  dplyr::mutate(
    desirability = desirability,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
   layout(title = 'The Philippines', textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11),
         xaxis = xaxis,
         yaxis = yaxis)
desi_combi  
```
 </div>
  
  <div class="col-md-4" markdown="1">
<br>  
**Remarks** 
<br>

* Effect of message 'no fees' clearly visible in former ING Direct countries
* What a good position in this plot is depends of the competition. Countries with a good position: Australia, Germany, Italy, The Netherlands, Romania, Spain
* *Data Januari 2020*

   </div> <div class="row">  
</div> 

  <div class="col-md-4" markdown="1">  <br> 
  
### All Countries
```{r overview Desirability, echo=F, eval=T, fig.width=4, fig.height=4, warning =F}
desi_price <- test %>%
  dplyr::select(quarter_measurement, labels_countries, b_value, desirability, label, price_mean) %>%
  dplyr::filter(quarter_measurement == 20 & b_value==1) %>%
  dplyr::mutate(
    desirability = desirability,
    price = price_mean *100
    ) %>%
  distinct()

xaxis <- list(title = "Price perception", 
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(20,80),
              dtick = 10,
              showline = TRUE,
              showgrid = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))
yaxis <- list(title = "Desirability",
              titlefont = list(color = 'rgb(105, 105, 105)', size = 12, family = "ING me"),
              range =c(0,50),
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              dtick = 5,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 1,
              #ticklen = 1,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(105, 105, 105)'))

desi_pricep <- desi_price %>%
  plot_ly(x = ~desi_price$price, y = ~desi_price$desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~desi_price$labels_countries, textposition = 'middle right',
           textfont = list(family = "ING me", color = 'rgb(105, 105, 105)', size = 11)) %>%
  layout(title = '',
         xaxis = xaxis,
         yaxis = yaxis)
desi_pricep 
```
</div>
  <div class="col-md-8" markdown="1">
  <br><br>
  
**Remarks** 
<br>  

* This graph confirms the country results. 
* The absolute position is depended of the market situation. 
* Spain holds a very strong position. 

  </div> <div class="row">  
</div>





  <div class="col-md-8" markdown="1">  <br> 
  
### Correlation with desirability

```{r corr, echo=F, eval=T, fig.width=8, fig.height=4, warning =F, message=F}
trial <- result %>%
  dplyr::select(X1, quarter_measurement, country, weight, b_value, price_perception_value, 
                desirability_value, easy_value, Love_ING, digital_experience_value) %>%
  dplyr::filter(b_value <10 & !is.na(desirability_value) & !is.na(price_perception_value)) %>%
  dplyr::mutate(
    desi = desirability_value * weight,
    price = price_perception_value * weight,
    easy = easy_value * weight,
    digi = digital_experience_value * weight,
    love = Love_ING * weight)

trial_cor_AUS <- trial %>%
  dplyr::filter(country==1) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Australia = desi
  ) %>%
  dplyr::select(rowname, Australia)

trial_cor_AUT <- trial %>%
  dplyr::filter(country==2) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Austria = desi
  ) %>%
  dplyr::select(rowname, Austria)

trial_cor_BEL <- trial %>%
  dplyr::filter(country==3) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Belgium = desi
  ) %>%
  dplyr::select(rowname, Belgium)

trial_cor_CZ <- trial %>%
  dplyr::filter(country==4) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Czech = desi
  ) %>%
  dplyr::select(rowname, Czech)

trial_cor_FR <- trial %>%
  dplyr::filter(country==5) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    France = desi
  ) %>%
  dplyr::select(rowname, France)

trial_cor_GER <- trial %>%
  dplyr::filter(country==6) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Germany = desi
  ) %>%
  dplyr::select(rowname, Germany)

trial_cor_ITA <- trial %>%
  dplyr::filter(country==7) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Italy = desi
  ) %>%
  dplyr::select(rowname, Italy)

trial_cor_LUX <- trial %>%
  dplyr::filter(country==8) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Luxembourg = desi
  ) %>%
  dplyr::select(rowname, Luxembourg)

trial_cor_NL <- trial %>%
  dplyr::filter(country==9) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Netherlands = desi
  ) %>%
  dplyr::select(rowname, Netherlands)

trial_cor_POL <- trial %>%
  dplyr::filter(country==10) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Poland = desi
  ) %>%
  dplyr::select(rowname, Poland)

trial_cor_ROM <- trial %>%
  dplyr::filter(country==11) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Romania = desi
  ) %>%
  dplyr::select(rowname, Romania)

trial_cor_SPA <- trial %>%
  dplyr::filter(country==12) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Spain = desi
  ) %>%
  dplyr::select(rowname, Spain)

trial_cor_TUR <- trial %>%
  dplyr::filter(country==13) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Turkey = desi
  ) %>%
  dplyr::select(rowname, Turkey)

trial_cor_PH <- trial %>%
  dplyr::filter(country==14) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Philippines = desi
  ) %>%
  dplyr::select(rowname, Philippines)

df_list <- list(trial_cor_AUS, 
                trial_cor_AUT,
                trial_cor_BEL,
                trial_cor_CZ,
                trial_cor_FR,
                trial_cor_GER,
                trial_cor_ITA,
                trial_cor_LUX,
                trial_cor_NL,
                trial_cor_POL,
                trial_cor_PH,
                trial_cor_TUR,
                trial_cor_SPA,
                trial_cor_ROM) 

cortab <- Reduce(function(d1, d2) merge(d1, d2, by = "rowname", all.x = TRUE, all.y = FALSE), 
       df_list)
cortab <- cortab[-c(1,2,3,5,7,9,11,12,13),]

# Transpose data
cortab <- as.data.frame(t(cortab))
colnames(cortab) = as.character(unlist(cortab[1,]))
cortab$country <-rownames(cortab)
cortab = cortab[-1,]
rownames(cortab) <- NULL
cortab <- as.tibble(cortab)
cortab$digi <- as.numeric(as.character(cortab$digi))
cortab$easy <- as.numeric(as.character(cortab$easy))
cortab$love <- as.numeric(as.character(cortab$love))
cortab$price_perception_value <- as.numeric(as.character(cortab$price_perception_value))

r <- plot_ly(
  type = 'table',
  columnwidth = c(70, 40, 40, 40),
  columnorder = c(0, 1, 2, 3),
  header = list(
    values = c("country", "easy", "love", "price"),
    align = c("center", "center", "center", "center", "center"),
    line = list(width = 1, color = c("rgb 168, 168, 168")),
    fill = list(color = c("rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)",
                          "rgb(255,098,000)", "rgb(255,098,000)")),
    font = list(family = "ING me", size = 14, color = "white")
    ),
  cells = list(values = rbind(cortab$country, 
                              #cortab$digi, 
                              cortab$easy, 
                              cortab$love, 
                              cortab$price_perception_value),
    align = c("center", "center", "center", "center", "center"),
    line = list(color = c("rgb 168, 168, 168"), width = 1),
    font = list(family = "ING me", size = 12, color = c("rgb 105, 105, 105"))))
r
```
</div>
  <div class="col-md-4" markdown="1">
  <br><br>
 
**Remarks** 
<br>  

* This table shows the correlation between the digital experience, how easy the banks are perceived, love, price perceptopn and desirability. 
* These results show correlations regardless of the brand. 
* The most important conclusion is that there is a strong relationship between how easy the brands are perceived and desirability. 
* The results do not proof a (negative) relationship between price perception and desirability. Because of the question behind desirability, this is in line with expectation. 

check whether other scales need to be standardized



  </div>
</div>


  <div class="col-md-8" markdown="1">  <br> 
  
### Correlation with desirability for ING specifically

```{r corri, echo=F, eval=T, fig.width=8, fig.height=4, warning =F, message=F}
trial2 <- result %>%
  dplyr::select(X1, quarter_measurement, country, weight, b_value, price_perception_value, 
                desirability_value, easy_value, Love_ING, digital_experience_value) %>%
  dplyr::filter(b_value ==1 & !is.na(desirability_value) & !is.na(price_perception_value)) %>%
  dplyr::mutate(
    desi = desirability_value * weight,
    price = price_perception_value * weight,
    easy = easy_value * weight,
    digi = digital_experience_value * weight,
    love = Love_ING * weight)

trial_cor_AUS <- trial2 %>%
  dplyr::filter(country==1) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Australia = desi
  ) %>%
  dplyr::select(rowname, Australia)

trial_cor_AUT <- trial2 %>%
  dplyr::filter(country==2) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Austria = desi
  ) %>%
  dplyr::select(rowname, Austria)

trial_cor_BEL <- trial2 %>%
  dplyr::filter(country==3) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Belgium = desi
  ) %>%
  dplyr::select(rowname, Belgium)

trial_cor_CZ <- trial2 %>%
  dplyr::filter(country==4) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Czech = desi
  ) %>%
  dplyr::select(rowname, Czech)

trial_cor_FR <- trial2 %>%
  dplyr::filter(country==5) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    France = desi
  ) %>%
  dplyr::select(rowname, France)

trial_cor_GER <- trial2 %>%
  dplyr::filter(country==6) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Germany = desi
  ) %>%
  dplyr::select(rowname, Germany)

trial_cor_ITA <- trial2 %>%
  dplyr::filter(country==7) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Italy = desi
  ) %>%
  dplyr::select(rowname, Italy)

trial_cor_LUX <- trial2 %>%
  dplyr::filter(country==8) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Luxembourg = desi
  ) %>%
  dplyr::select(rowname, Luxembourg)

trial_cor_NL <- trial2 %>%
  dplyr::filter(country==9) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Netherlands = desi
  ) %>%
  dplyr::select(rowname, Netherlands)

trial_cor_POL <- trial2 %>%
  dplyr::filter(country==10) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Poland = desi
  ) %>%
  dplyr::select(rowname, Poland)

trial_cor_ROM <- trial2 %>%
  dplyr::filter(country==11) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Romania = desi
  ) %>%
  dplyr::select(rowname, Romania)

trial_cor_SPA <- trial2 %>%
  dplyr::filter(country==12) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Spain = desi
  ) %>%
  dplyr::select(rowname, Spain)

trial_cor_TUR <- trial2 %>%
  dplyr::filter(country==13) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Turkey = desi
  ) %>%
  dplyr::select(rowname, Turkey)

trial_cor_PH <- trial2 %>%
  dplyr::filter(country==14) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
                -desirability_value, -easy_value, -Love_ING, -digital_experience_value, -digi,-easy, -love, mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Philippines = desi
  ) %>%
  dplyr::select(rowname, Philippines)

df_list <- list(trial_cor_AUS, 
                trial_cor_AUT,
                trial_cor_BEL,
                trial_cor_CZ,
                trial_cor_FR,
                trial_cor_GER,
                trial_cor_ITA,
                trial_cor_LUX,
                trial_cor_NL,
                trial_cor_POL,
                trial_cor_PH,
                trial_cor_TUR,
                trial_cor_SPA,
                trial_cor_ROM) 

cortab <- Reduce(function(d1, d2) merge(d1, d2, by = "rowname", all.x = TRUE, all.y = FALSE), 
       df_list)
cortab <- cortab[-c(1,2,3,5,7,9,11,12,13),]

# Transpose data
cortab <- as.data.frame(t(cortab))
colnames(cortab) = as.character(unlist(cortab[1,]))
cortab$country <-rownames(cortab)
cortab = cortab[-1,]
rownames(cortab) <- NULL
cortab <- as.tibble(cortab)
cortab$digi <- as.numeric(as.character(cortab$digi))
cortab$easy <- as.numeric(as.character(cortab$easy))
cortab$love <- as.numeric(as.character(cortab$love))
cortab$price_perception_value <- as.numeric(as.character(cortab$price_perception_value))

r2 <- plot_ly(
  type = 'table',
  columnwidth = c(70, 40, 40, 40),
  columnorder = c(0, 1, 2, 3),
  header = list(
    values = c("country","easy", "love", "price"),
    align = c("center", "center", "center", "center", "center"),
    line = list(width = 1, color = c("rgb 168, 168, 168")),
    fill = list(color = c("rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)",
                          "rgb(255,098,000)", "rgb(255,098,000)")),
    font = list(family = "ING me", size = 14, color = "white")
    ),
  cells = list(values = rbind(cortab$country, 
                              #cortab$digi, 
                              cortab$easy, 
                              cortab$love, 
                              cortab$price_perception_value),
    align = c("center", "center", "center", "center", "center"),
    line = list(color = c("rgb 168, 168, 168"), width = 1),
    font = list(family = "ING me", size = 12, color = c("rgb 105, 105, 105"))))
r2
```
</div>
  <div class="col-md-4" markdown="1">
  <br><br>
  
**Remarks** 
<br>

* Results for ING specifically show equal correlations.
* There seems to be a somewhat stronger relationship between love and desirability.


   </div> <div class="row">  
</div>


  <div class="col-md-8" markdown="1">  <br> 
  
### Correlation with preference

```{r corrp, echo=F, eval=T, fig.width=8, fig.height=4, warning =F, message=F}
trialp <- result %>%
  dplyr::select(X1, quarter_measurement, country, weight, b_value, price_perception_value, 
                desirability_value, easy_value, Love_ING, digital_experience_value,
                preference_value, smart_value, meets_needs_value,) %>%
  dplyr::filter(!is.na(preference_value) & !is.na(price_perception_value)) %>%
  dplyr::mutate(
    desi = desirability_value * weight,
    price = price_perception_value * weight,
    easy = easy_value * weight,
    digi = digital_experience_value * weight,
    love = Love_ING * weight,
    preference = preference_value * weight,
    smart = smart_value * weight,
    meets_needs = meets_needs_value * weight)

trial_cor_AUSp <- trialp %>%
  dplyr::filter(country==1) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Australia = preference
  ) %>%
  dplyr::select(rowname, Australia)

trial_cor_AUTp <- trialp %>%
  dplyr::filter(country==2) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Austria = preference
  ) %>%
  dplyr::select(rowname, Austria)

trial_cor_BELp <- trialp %>%
  dplyr::filter(country==3) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Belgium = preference
  ) %>%
  dplyr::select(rowname, Belgium)

trial_cor_CZp <- trialp %>%
  dplyr::filter(country==4) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Czech = preference
  ) %>%
  dplyr::select(rowname, Czech)

trial_cor_FRp <- trialp %>%
  dplyr::filter(country==5) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    France = preference
  ) %>%
  dplyr::select(rowname, France)

trial_cor_GERp <- trialp %>%
  dplyr::filter(country==6) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Germany = preference
  ) %>%
  dplyr::select(rowname, Germany)

trial_cor_ITAp <- trialp %>%
  dplyr::filter(country==7) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Italy = preference
  ) %>%
  dplyr::select(rowname, Italy)

trial_cor_LUXp <- trialp %>%
  dplyr::filter(country==8) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Luxembourg = preference
  ) %>%
  dplyr::select(rowname, Luxembourg)

trial_cor_NLp <- trialp %>%
  dplyr::filter(country==9) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Netherlands = preference
  ) %>%
  dplyr::select(rowname, Netherlands)

trial_cor_POLp <- trialp %>%
  dplyr::filter(country==10) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Poland = preference
  ) %>%
  dplyr::select(rowname, Poland)

trial_cor_ROMp <- trialp %>%
  dplyr::filter(country==11) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Romania = preference
  ) %>%
  dplyr::select(rowname, Romania)

trial_cor_SPAp <- trialp %>%
  dplyr::filter(country==12) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Spain = preference
  ) %>%
  dplyr::select(rowname, Spain)

trial_cor_TURp <- trialp %>%
  dplyr::filter(country==13) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Turkey = preference
  ) %>%
  dplyr::select(rowname, Turkey)

trial_cor_PHp <- trialp %>%
  dplyr::filter(country==14) %>%
  correlate() %>% 
    focus(-X1, -quarter_measurement, -country, -weight, -b_value, -price_perception_value, 
          -desirability_value, -easy_value, -Love_ING, -digital_experience_value,
          -digi,-easy, -love, -preference_value, -smart_value, -meets_needs_value,
          mirror= FALSE) %>%
  fashion() %>%
  dplyr::mutate(
    Philippines = preference
  ) %>%
  dplyr::select(rowname, Philippines)

df_listp <- list(trial_cor_AUSp, 
                trial_cor_AUTp,
                trial_cor_BELp,
                trial_cor_CZp,
                trial_cor_FRp,
                trial_cor_GERp,
                trial_cor_ITAp,
                trial_cor_LUXp,
                trial_cor_NLp,
                trial_cor_POLp,
                trial_cor_PHp,
                trial_cor_TURp,
                trial_cor_SPAp,
                trial_cor_ROMp) 

cortabp <- Reduce(function(d1, d2) merge(d1, d2, by = "rowname", all.x = TRUE, all.y = FALSE),
       df_listp)
cortabp <- cortabp[-c(1,2,4,5,8,13,15,16),]

# Transpose data
cortabp <- as.data.frame(t(cortabp))
colnames(cortabp) = as.character(unlist(cortabp[1,]))
cortabp$country <-rownames(cortabp)
cortabp = cortabp[-1,]
rownames(cortabp) <- NULL
cortabp <- as.tibble(cortabp)
#cortabp$digi <- as.numeric(as.character(cortabp$digi))
cortabp$easy <- as.numeric(as.character(cortabp$easy))
cortabp$love <- as.numeric(as.character(cortabp$love))
cortabp$price_perception_value <- as.numeric(as.character(cortabp$price_perception_value))

r2p <- plot_ly(
  type = 'table',
  columnwidth = c(70, 40, 40, 40),
  columnorder = c(0, 1, 2, 3),
  header = list(
    values = c("country", "easy", "love", "price"),
    align = c("center", "center", "center", "center", "center"),
    line = list(width = 1, color = c("rgb 168, 168, 168")),
    fill = list(color = c("rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)",
                          "rgb(255,098,000)", "rgb(255,098,000)")),
    font = list(family = "ING me", size = 14, color = "white")
    ),
  cells = list(values = rbind(cortabp$country, 
                             # cortabp$digi, 
                              cortabp$easy, 
                              cortabp$love, 
                              cortabp$price_perception_value),
    align = c("center", "center", "center", "center", "center"),
    line = list(color = c("rgb 168, 168, 168"), width = 1),
    font = list(family = "ING me", size = 12, color = c("rgb 105, 105, 105"))))
r2p
```
</div>
  <div class="col-md-4" markdown="1">
  <br><br>
  
**Remarks** 
<br>


* It is relevant to explore the relation between price and preference, as desirability excludes the price factor in the question. 
* There seems to be no relation with the first 3 variables, these results might not completely true, as the level of the variable preference is completely different. 
* Analysis must be repeated when the variables are standardized to get a better understanding of these correlation. 
* These results already indicate a negative correlation between price and preference. 


  </div> <div class="row">  
</div>

  <div class="col-md-8" markdown="1">  <br> 
  
### Correlation with preference - more variables


density <- density((result$desirability_value, na.rm=T)

fig <- plot_ly(x = ~density$x, y = ~density$y, type = 'scatter', mode = 'lines', fill = 'tozeroy')
fig <- fig %>% layout(xaxis = list(title = 'desi'),
         yaxis = list(title = 'Density'))

fig

```{r corrpr, echo=F, eval=T, fig.width=8, fig.height=4, warning =F, message=F}
trialpr <- result %>%
  dplyr::select(X1, quarter_measurement, country, weight, b_value, price_perception_value, 
                desirability_value, easy_value, Love_ING, smart_value, meets_needs_value,
                preference_value, digital_experience_value) %>%
  dplyr::filter(!is.na(preference_value) & !is.na(price_perception_value)) %>%
  dplyr::mutate(
    desi = desirability_value * weight,
    price = price_perception_value * weight,
    easy = easy_value * weight,
    digi = digital_experience_value * weight,
    love = Love_ING * weight,
    preference = preference_value * weight,
    smart = smart_value * weight,
    meets_needs = meets_needs_value * weight,
    )

den_AUS <- density(trialpr$desirability_value[trialpr$country==1], na.rm=T)
den_AUT <- density(trialpr$desirability_value[trialpr$country==2], na.rm=T)
den_BEL <- density(trialpr$desirability_value[trialpr$country==3], na.rm=T)
den_CZE <- density(trialpr$desirability_value[trialpr$country==4], na.rm=T)
den_GER <- density(trialpr$desirability_value[trialpr$country==5], na.rm=T)
den_FRA <- density(trialpr$desirability_value[trialpr$country==6], na.rm=T)
den_ITA <- density(trialpr$desirability_value[trialpr$country==7], na.rm=T)
den_LUX <- density(trialpr$desirability_value[trialpr$country==8], na.rm=T)
den_NLD <- density(trialpr$desirability_value[trialpr$country==9], na.rm=T)
den_POL <- density(trialpr$desirability_value[trialpr$country==10], na.rm=T)
den_ROM <- density(trialpr$desirability_value[trialpr$country==11], na.rm=T)
den_SPA <- density(trialpr$desirability_value[trialpr$country==12], na.rm=T)
den_TUR <- density(trialpr$desirability_value[trialpr$country==13], na.rm=T)
den_PHI <- density(trialpr$desirability_value[trialpr$country==14], na.rm=T)

figAUS <- plot_ly(
  x = ~den_AUS$x, y = ~den_AUS$y, type = 'scatter', mode = 'lines', fill = 'tozeroy') %>% layout(xaxis = list(title = 'Desirability'),
                      yaxis = list(title = 'Density'))

figAUS


figAUT <- plot_ly(
  x = ~den_AUT$x, y = ~den_AUT$y, type = 'scatter', mode = 'lines', fill = 'tozeroy') %>% layout(xaxis = list(title = 'Desirability'),
                      yaxis = list(title = 'Density'))

figAUT 
  
figTUR <- plot_ly(
  x = ~den_TUR$x, y = ~den_TUR$y, type = 'scatter', mode = 'lines', fill = 'tozeroy') %>% layout(xaxis = list(title = 'Desirability'),
                      yaxis = list(title = 'Density'))

figTUR 

```
