---
title: "Communication & Brand experience update"
output: ingmarkdowntemplates::ing_html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Management summary results Q1 2020

This document provides you an overview of the KPI's of the CoE Communications and Brand Experience. 

## Desirability

```{r overview Desirability, echo=F, eval=T}
desi <- data %>%
  dplyr::select(quarter_measurement, country, b_value, desirability) %>%
  dplyr::filter(quarter_measurement >17 & b_value==1) %>%
  dplyr::mutate(
    desirability = desirability *100
    ) %>%
  distinct()

desi_CAGR <- data %>%
  dplyr::select(quarter_measurement, country, b_value, desirability) %>%
  dplyr::filter(quarter_measurement >17 & b_value==1) %>%
  dplyr::mutate(
    desirability = desirability *100
    ) %>%
  distinct() %>% 
  # Spread across quarters
  tidyr::spread(quarter_measurement, desirability) %>% 
  # Calculate CAGR
  dplyr::mutate(
    cagr = (`20`/`18`)^(1/3) - 1
  ) %>% 
  # Gather across quarters
  tidyr::gather(quarter_measurement, desirability, -country, -b_value, -cagr) %>% 
  # Filter to per country per time
  dplyr::select(country, cagr) %>% 
  dplyr::distinct()

c <- c("Australia", "Austria", "Belgium", "Czech", "France", "Germany", "Italy", "Luxembourg", 
       "Netherlands", "Poland", "Romania", "Spain", "Turkey", "The Philippines")

desi_p<- plot_ly(
  type = 'table',
  columnwidth = c(70, 40, 40, 40, 40),
  columnorder = c(0, 1, 2, 3, 4),
  header = list(
    values = c("country","Q2 2019", "Q3 2019", "Q4 2019", "CAGR"),
    align = c("center", "center", "center", "center", "center"),
    line = list(width = 1, color = c("rgb 168, 168, 168")),
    fill = list(color = c("rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)")),
    font = list(family = "ING me", size = 14, color = "white")
  ),
  cells = list(
    values = rbind(c,
                   round(desi$desirability[desi$quarter_measurement==18], digits=2),
                   round(desi$desirability[desi$quarter_measurement==19], digits=2), 
                   round(desi$desirability[desi$quarter_measurement==20], digits=2),
                   round(desi_CAGR$cagr, digits=2)),
    align = c("center", "center", "center", "center", "center"),
    line = list(color = c("rgb 168, 168, 168"), width = 1),
    font = list(family = "ING me", size = 12, color = c("rgb 105, 105, 105"))
  ))
desi_p
```

CAGR: Compound annual growth rate, i.e. constant % variance period-on-period for the periods presented (3)

## Reputation pulse score
```{r overview Reputation, echo=F, eval=T}

rep <- data %>%
  dplyr::select(quarter_measurement, country, b_value, pulse) %>%
  dplyr::filter(quarter_measurement > 16 & b_value==1) %>%
  dplyr::mutate(
    pulse = pulse *100
  ) %>%
  distinct()

rep_CAGR <- data %>%
  dplyr::select(quarter_measurement, country, b_value, pulse) %>%
  dplyr::filter(quarter_measurement >17 & b_value==1) %>%
  dplyr::mutate(
    pulse = pulse *100
  ) %>%
  distinct() %>% 
  # Spread across quarters
  tidyr::spread(quarter_measurement, pulse) %>% 
  # Calculate CAGR
  dplyr::mutate(
    cagr = (`20`/`18`)^(1/3) - 1
  ) %>% 
  # Gather across quarters
  tidyr::gather(quarter_measurement, pulse, -country, -b_value, -cagr) %>% 
  # Filter to per country per time
  dplyr::select(country, cagr) %>% 
  dplyr::distinct()

c <- c("Australia", "Austria", "Belgium", "Czech", "France", "Germany", "Italy", "Luxembourg", 
       "Netherlands", "Poland", "Romania", "Spain", "Turkey", "The Philippines")

r <- plot_ly(
  type = 'table',
  columnwidth = c(70, 40, 40, 40, 40),
  columnorder = c(0, 1, 2, 3, 4),
  header = list(
    values = c("country","Q2 2019", "Q3 2019", "Q4 2019", "CAGR"),
    align = c("center", "center", "center", "center", "center"),
    line = list(width = 1, color = c("rgb 168, 168, 168")),
    fill = list(color = c("rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)")),
    font = list(family = "ING me", size = 14, color = "white")
  ),
  cells = list(
    values = rbind(c, round(rep$pulse[rep$quarter_measurement==18], digits=2),
                   round(rep$pulse[rep$quarter_measurement==19], digits=2), 
                   round(rep$pulse[rep$quarter_measurement==20], digits=2),
                   round(rep_CAGR$cagr, digits=2)),
    align = c("center", "center", "center", "center", "center"),
    line = list(color = c("rgb 168, 168, 168"), width = 1),
    font = list(family = "ING me", size = 12, color = c("rgb 105, 105, 105"))
  ))
r
```
## Internal NPS
```{r overview Internal NPS, echo=F, eval=T}

```
## Australia
### Brand funnel
```{r Australia brand funnel, echo=F, eval=T}
par(mfrow = c(1, 2))
funnel_data <- data %>%
  dplyr::select(unaided, toma, aided, fami, opinion, consideration, preference, quarter_measurement, b_value, country) %>%
  dplyr::filter(quarter_measurement ==20 & country==1) %>%
  dplyr::mutate(
    unaided_best = max(unaided, na.rm=T) *100, 
    aided_best = max(aided, na.rm=T) * 100, 
    toma_best = max(toma, na.rm=T) * 100, 
    fami_best = max(fami, na.rm=T) * 100, 
    opinion_best = max(opinion, na.rm=T) * 100, 
    consideration_best = max(consideration, na.rm=T) * 100, 
    preference_best = max(preference, na.rm=T) * 100, 
    unaided = unaided * 100,
    aided = aided * 100,
    toma = toma * 100,
    fami = fami * 100,
    consideration = consideration *100,
    preference = preference *100,
  ) %>%
  dplyr::distinct() 

funnel_data_diff <- funnel_data %>%
  dplyr::select(unaided_best, aided_best, toma_best, fami_best, opinion_best, 
                consideration_best, preference_best, unaided, aided, toma, fami, 
                opinion, consideration, preference, b_value, quarter_measurement, country) %>%
  dplyr::mutate(
    diff_aided = dplyr::case_when(
      b_value==1 ~ (aided_best - aided),
      TRUE ~ 0),
    diff_fami = dplyr::case_when(
      b_value==1 ~ (fami_best - fami),
      TRUE ~ 0),
    diff_cons = dplyr::case_when(
      b_value==1 ~ (consideration_best - consideration),
      TRUE ~ 0),
    diff_pref = dplyr::case_when(
      b_value==1 ~ (preference_best - preference),
      TRUE ~ 0),
    ) %>%
  dplyr::filter(diff_aided!=0, diff_fami!=0, diff_cons!=0, diff_pref!=0)

par(mfrow = c(1, 2))

funnel_data <- funnel_data %>%
  dplyr::filter(b_value==1)
funnel_data %>%
  plot_ly() %>%
  add_trace(type = "funnel",
            y = c("Aided", "Familiarity", "Consideration", "Preference"),
            x = c(round(funnel_data$aided, digits=2), round(funnel_data$fami, digits=2), 
                  round(funnel_data$consideration, digits=2), round(funnel_data$preference, digits=2)),
            textposition = "inside",
            textinfo = "value",
            opacity = 1.0,
            marker = list(color = c("rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)", "rgb(255,098,000)"),
                          line = list(width = c(2, 2, 2, 2), color = c("white", "white", "white", "white"))),
            textfont = list(family = "ING me", size = 14, color = "white"),
            connector = list(line = list(color = "white"))) %>%
  layout(yaxis = list(categoryarray = c("Aided", "Familiarity", "Consideration", "Preference")))

tab <- plot_ly(
  type = 'table',
  columnwidth = c(1),
  columnorder = c(0),
  header = list(
    values = c("delta best comp"),
    align = c("center"),
    line = list(width = 1, color = 'black'),
    fill = list(color = "rgb(255,098,000)"),
    font = list(family = "ING me", size = 14, color = "white")
  ),
  cells = list(
    values = cbind(round(funnel_data_diff$diff_aided, digits=2),
                   round(funnel_data_diff$diff_fami, digits=2),
                   round(funnel_data_diff$diff_cons, digits=2),
                   round(funnel_data_diff$diff_pref, digits=2)),
    align = c("center", "center", "center", "center"),
    line = list(color = c("rgb 168, 168, 168"), width = 1),
    font = list(family = "ING me", size = 12, color = c("rgb 105, 105, 105"))
  ))
tab
```

ING is still behind the best competitor regarding awareness, which is translated to the lower level of the funnel as well. 

### Love
```{r Australia love, echo=F, eval=T}
love <- data %>%
  dplyr::select(quarter_measurement, country, love_mean_ING, love_mean_Google, love_mean_ING_client) %>%
  dplyr::filter(quarter_measurement >17 & country==1) %>%
  distinct()

xaxis <- list(title = "",
              showline = TRUE,
              showgrid = FALSE,
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 2,
              ticklen = 5,
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(204, 204, 204)'))

yaxis <- list(title = "",
              showgrid = FALSE,
              zeroline = FALSE,
              showline = FALSE,
              showticklabels = FALSE,
              range =c(0,10))
margin <- list(autoexpand = F)

# Build the annotations

love_ING_clients <- list(
  xref = '',
  yref = '',
  x = 0.05,
  y = love$love_mean_ING_client[1],
  xanchor = 'right',
  yanchor = 'middle',
  text = ~paste('love ING clients ', love_mean_ING_client[1], '%'),
  font = list(family = 'ING me',
              size = 16,
              color = 'rgb(255,098,000)'),
  showarrow = FALSE)

love_mean_ING <- list(
  xref = '',
  yref = '',
  x = 0.05,
  y = love$love_mean_ING[1],
  xanchor = 'right',
  yanchor = 'middle',
  text = ~paste('love ING general pop', love_mean_ING[1], '%'),
  font = list(family = 'ING me',
              size = 16,
              color = c('rgb(52, 150, 81')),
  showarrow = FALSE)

love_mean_Google <- list(
  xref = 'paper',
  x = 0.95,
  y = love$love_mean_Google[1],
  xanchor = 'left',
  yanchor = 'middle',
  text = paste('love Google', love$love_mean_Google[1], '%'),
  font = list(family = 'ING me',
              size = 16,
              color = 'rgb(82,81,153)'),
  showarrow = FALSE)

love$x <-c("Q2 2019", "Q3 2019", "Q4 2019")
l<-love %>%
  plot_ly(x = ~x) %>%
  add_lines(y = ~love_mean_ING_client, type='scatter', name='love ING clients', 
            line = list(color = 'rgb(255,098,000)', type='scatter', width = 4, mode = 'lines+markers')) %>%
  add_lines(y =~love_mean_Google, type='scatter', name='love Google',
            line = list(color = 'rgb(82,81,153)', width = 4, mode = 'lines+markers')) %>%
  add_lines(y =~love_mean_ING, type='scatter', name='love ING',
            line = list(color = 'rgb(52, 150, 81', width = 4, mode = 'lines+markers')) %>%
  layout(title = "Love scores",
         xaxis = xaxis,
         yaxis = yaxis)
l
```

Australia has shown stable love scores since last quarter. 

### Desirability and price perception

```{r Australia Desirability vs price perception, echo=F, eval=T, warning=F}
desi_comb <- data %>%
  dplyr::select(quarter_measurement, country, label, desirability, price_mean) %>%
  dplyr::filter(quarter_measurement ==20 & country==1) %>%
  dplyr::mutate(
    desirability = desirability *100,
    price_mean = price_mean *100
  ) %>%
  distinct()

xaxis <- list(title = "Price perception",
              showline = TRUE,
              showgrid = FALSE,
              showticklabels = TRUE,
              linecolor = 'rgb(204, 204, 204)',
              linewidth = 2,
              autotick = FALSE,
              ticks = 'inside',
              tickcolor = 'rgb(204, 204, 204)',
              tickwidth = 2,
              ticklen = 5,
              #range = c(20, 80), 
              seq(0, 100, by = 10),
              tickfont = list(family = "ING me",
                              size = 12,
                              color = 'rgb(204, 204, 204)'))

desi_combi <- desi_comb %>%
  plot_ly(x = ~price_mean, y = ~desirability, type = 'scatter', color ='rgb(255,098,000)',
           mode = 'text+markers', text = ~label, textposition = 'middle right',
           textfont = list(color = 'rgb(204, 204, 204)', size = 11)) %>%
  layout(title = 'Q4 2019',
         xaxis = xaxis,
         yaxis = list(title = 'Desirability',
                      range = c(0, 50)
                      ))
desi_combi  
```

Commonwealth is the most desired brand in the market, closely followed by ING. It is an important advantage that ING is not considered as expensive. 

### Reputation
```{r Australia pulse, echo=F, eval=T}
rep_brand <- data %>%
  dplyr::select(quarter_measurement, country, b_value, pulse) %>%
  dplyr::filter(quarter_measurement > 16 & country==1 & b_value <6) %>%
  dplyr::mutate(
    pulse = pulse *100
  ) %>%
  distinct() %>%
  # Gather across brands
  tidyr::spread(b_value, pulse) 

rep_brand$x <-c("Q1 2019", "Q2 2019", "Q3 2019", "Q4 2019")
rep_b<-rep_brand %>%
  plot_ly(x = ~x) %>%
  add_lines(y = ~rep_brand$'1', type='scatter', name='ING',
            line = list(color = 'rgb(255,098,000)', type='scatter', width = 4, mode = 'lines+markers')) %>%
  add_lines(y =~rep_brand$'2', type='scatter', name='ANZ',
            line = list(color = 'rgb(96,166,218)', width = 4, mode = 'lines+markers')) %>%
  add_lines(y =~rep_brand$'3', type='scatter', name='Commonwealth Bank',
            line = list(color = 'rgb(171,0,102)', width = 4, mode = 'lines+markers')) %>%
  add_lines(y =~rep_brand$'4', type='scatter', name='NAB',
            line = list(color = 'rgb(208,217,60)', width = 4, mode = 'lines+markers')) %>%
  add_lines(y =~rep_brand$'5', type='scatter', name='Westpac',
          line = list(color = 'rgb(52,150,81)', width = 4, mode = 'lines+markers')) %>%
  layout(title = "Pulse",
         xaxis = list(title = "quarters"),
         yaxis = list(title = "", range= c(0,100))
  )
rep_b
```
